---
title: "CT RTGTFS: Speed Analysis Tool"

output:
  flexdashboard::flex_dashboard
    # theme: 
    #   version: 4
    #   bootswatch: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width = "100%")
# knitr::opts_chunk$set(
#   cache = FALSE, cache.lazy = FALSE, autodep = TRUE, warning = FALSE, 
#   message = FALSE, echo = TRUE, dpi = 180,
#   fig.width = 5, fig.height = 3, echo = FALSE
#   )
```

<!--#general comments===========================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#
# This is [[insert description here - what it does/solve]]
#
# By: mike gaunt, michael.gaunt@wsp.com
#
# README: [[insert brief readme here]]
#-------- [[insert brief readme here]]
#
# *please use 80 character margins
# *please go to https://pkgs.rstudio.com/flexdashboard/articles/layouts.html
# to explore the different layouts available for the flexdashboard framework
#
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

<!--#library set-up=============================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev -->
```{r}
library(crosstalk)
library(leaflet)
```

<!--#source helpers/utilities===================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev -->
```{r}
source(here::here("code", "dev_dashboard_data_setup.r"))

mapviewOptions(homebutton = F)
```

<!--#source data================================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev 
#area to upload data with and to perform initial munging
#please add test data here so that others may use/unit test these scripts -->
```{js}
function filter_default(){
  document.getElementById("fltr_direction_id").getElementsByClassName("selectized")[0].selectize.setValue(["north_bound", "south_bound"],false)
  document.getElementById("fltr_flag_peak_time").getElementsByClassName("selectized")[0].selectize.setValue("PM Peak",false) 
  document.getElementById("fltr_flag_week_part").getElementsByClassName("selectized")[0].selectize.setValue("week_core",false)
}
    
$(document).ready(filter_default);
```


Corridor Speed Statistics  
================================================================================ 

 Column {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### Route Speed Profiles
```{r eval=TRUE}
windows = c(1, 3, 5, 7)
plot_data = data_speed_pro_stats %>%
  pivot_longer(cols = c("speed_avg_mean", contains("_qt_"))
               ,names_to = "speed_quantile") %>%
  filter(speed_quantile %in% c('speed_avg_mean', 'speed_avg_qt_0.05'  
                     ,'speed_avg_qt_0.5', 'speed_avg_qt_0.95')) %>%
  filter(direction_id == "north_bound") %>% 
  group_by(flag_peak_time, speed_quantile) %>%  
  mutate(across(
    value
    ,purrr::map(windows
                ,~purrr::partial(zoo::rollmean, k = .x, align = "center", na.pad = T))
    ,.names = "MA {windows}")) %>% 
  ungroup() %>% 
  pivot_longer(cols = contains("MA")
               ,names_to = "smoothing_window"
               ,values_to = "value_sm") %>% 
  select(index:direction_id, speed_quantile, smoothing_window, value_sm)

plot_temp = plot_data %>% 
  mutate(speed_quantile = str_remove(speed_quantile, "speed_avg_")
         ,label = str_glue("Seg Speed: {gauntlet::dgt2(value_sm)} ({smoothing_window})\nStatistic: {speed_quantile}\n{direction_id}\nRoute Segement: {index}")
  ) %>% 
  filter(smoothing_window  %in% paste0('MA ', c(1, 7))) %>%
  filter(flag_peak_time != "Midday") %>%
  group_by(flag_peak_time) %>%
  group_map(~{
    plot_ly(.x, x=~index, y = ~value_sm, color = ~speed_quantile, legendgroup = ~speed_quantile
            ,text = ~label, hoverinfo = 'text'
            ,type = "scatter",  mode = 'lines', showlegend = (.y == "AM Peak")
            ,customdata = ~smoothing_window
            ,transforms = list(
              list(type = 'filter',target = ~smoothing_window, operation = '=',value = 'MA 1')
            )
    ) %>% 
      layout(yaxis = list(
        # range = c(0, max(.x$value)*1.1)
        titlefont = list(size = 11)
        ,title = paste0(
          c(rep("&nbsp;", 20),
            paste("<b>", as.character(.y), "</b>"),
            rep("&nbsp;", 20)),
          collapse = "")
        ,updatemenus = gauntlet::plty_make_menu_item(
          name_list = paste0("MA ", c(1,  5, 7))
          ,filter_pos = 0,direction = "right", x = 0, y = 1.2)
      )
      )
  })

tmp_nb = subplot(
  list(plot_temp[[1]], plot_temp[[2]]), #, plot_temp[[3]]),
  nrows = 2, margin = .05, shareX = T, shareY = T, titleY = T) %>%
  # rangeslider() %>% 
  layout(
    showlegend = T
    ,xaxis = list(title = "Route Segement Number")
    # yaxis = list(title = "Queired Date"),
    ,updatemenus = gauntlet::plty_make_menu_item(
      name_list = paste0("MA ", c(1, 7))
      ,filter_pos = 0,direction = "right", x = 0, y = 1.2)
  )

```

```{r eval=TRUE}
# windows = c(1, 3, 5, 7)
plot_data = data_speed_pro_stats %>%
  pivot_longer(cols = c("speed_avg_mean", contains("_qt_"))
               ,names_to = "speed_quantile") %>%
  filter(speed_quantile %in% c('speed_avg_mean', 'speed_avg_qt_0.05'  
                     ,'speed_avg_qt_0.5', 'speed_avg_qt_0.95')) %>%
  filter(direction_id != "north_bound") %>% 
  group_by(flag_peak_time, speed_quantile) %>%  
  mutate(across(
    value
    ,purrr::map(windows
                ,~purrr::partial(zoo::rollmean, k = .x, align = "center", na.pad = T))
    ,.names = "MA {windows}")) %>% 
  ungroup() %>% 
  pivot_longer(cols = contains("MA")
               ,names_to = "smoothing_window"
               ,values_to = "value_sm") %>% 
  select(index:direction_id, speed_quantile, smoothing_window, value_sm)

plot_temp = plot_data %>% 
  mutate(speed_quantile = str_remove(speed_quantile, "speed_avg_")
         ,label = str_glue("Seg Speed: {gauntlet::dgt2(value_sm)} ({smoothing_window})\nStatistic: {speed_quantile}\n{direction_id}\nRoute Segement: {index}")
  ) %>% 
  filter(smoothing_window  %in% paste0('MA ', c(1, 7))) %>%
  filter(flag_peak_time != "Midday") %>%
  group_by(flag_peak_time) %>%
  group_map(~{
    plot_ly(.x, x=~index, y = ~value_sm, color = ~speed_quantile, legendgroup = ~speed_quantile
            ,text = ~label, hoverinfo = 'text'
            ,type = "scatter",  mode = 'lines', showlegend = (.y == "AM Peak")
            ,customdata = ~smoothing_window
            ,transforms = list(
              list(type = 'filter',target = ~smoothing_window, operation = '=',value = 'MA 1')
            )
    ) %>% 
      layout(yaxis = list(
        # range = c(0, max(.x$value)*1.1)
        titlefont = list(size = 11)
        ,title = paste0(
          c(rep("&nbsp;", 20),
            paste("<b>", as.character(.y), "</b>"),
            rep("&nbsp;", 20)),
          collapse = "")
        ,updatemenus = gauntlet::plty_make_menu_item(
          name_list = paste0("MA ", c(1,  5, 7))
          ,filter_pos = 0,direction = "right", x = 0, y = 1.2)
      )
      )
  })

tmp_sb = subplot(
  list(plot_temp[[1]], plot_temp[[2]]), #, plot_temp[[3]]),
  nrows = 2, margin = .05, shareX = T, shareY = T, titleY = T) %>%
  # rangeslider() %>% 
  layout(
    showlegend = T
    ,xaxis = list(title = "Route Segement Number")
    # yaxis = list(title = "Queired Date"),
    ,updatemenus = gauntlet::plty_make_menu_item(
      name_list = paste0("MA ", c(1, 7))
      ,filter_pos = 0,direction = "right", x = 0, y = 1.2)
  )

```

```{r eval=TRUE}
crosstalk::bscols(
  widths = c(12, 12)
  ,tmp_nb
  ,tmp_sb
)
```

### Segment Summary Statistics
```{r eval=TRUE}
tmp_1 = data_speed_pro_stats %>%
  pivot_longer(cols = c("speed_avg_var", "speed_avg_sd", "speed_avg_stderr", "speed_avg_pre", "rec_count")) %>%
  group_by(flag_peak_time, name) %>%
  mutate(value = zoo::rollmean(value, k = 5, align = "center", na.pad = T) %>%
           dgt2()) %>%
  ungroup() %>%
  ggplot() +
  geom_line(aes(index, value, color = flag_peak_time), alpha = .6) +
  facet_grid(rows = vars(name), cols = vars(direction_id), scales = "free") +
  labs(x = "Route Segement Number", y = "Metric Value", color = "Week Part") +
  theme(legend.position = "bottom")

plotly::ggplotly(tmp_1)
```

Column {data-width=400} 
--------------------------------------------------------------------------------

### Route Segements
```{r}
data_map = list_speed_profiles$route_samples %>%
  filter(index >= min(index_selected$index) &
           index <= max(index_selected$index)) %>% 
  mutate(label = str_glue("Route Segment: {index}"))

data_map_sh = SharedData$new(data_map)

yolo = crosstalk::bscols(
  widths = c(6, 12)
  ,filter_slider("fltr_speed_avg", "Route Segement:", data_map_sh, ~index, step = 5, round = T)
  ,leaflet(height = 700) %>% 
    leaflet::addTiles(group = "OSM (default)") %>%
    leaflet::addCircleMarkers(
      data = data_map_sh, label = data_map$label %>% purrr::map(htmltools::HTML) 
      ,color = "blue", opacity = .5, fillOpacity  = .2, weight = 1, radius = 10)
)

```

```{r}
leaflet(height = 700) %>% 
    leaflet::addTiles(group = "OSM (default)") %>%
    leaflet::addCircleMarkers(
      data = data_map_sh, label = data_map$label %>% purrr::map(htmltools::HTML) 
      ,color = "blue", opacity = .5, fillOpacity  = .2, weight = 1, radius = 10) %>% 
  addMeasure(primaryLengthUnit = "meter", position = "bottomleft")
```

Raw Data 
================================================================================ 

Column 
--------------------------------------------------------------------------------

```{r}
library(crosstalk)

data_speed_pro_1 = data_speed_pro %>%  
  st_as_sf(coords = c("lon", "lat"), crs = 32610) %>%  
  st_transform(crs = 4326) %>% 
  gauntlet::st_extract_coords() %>%  
  st_drop_geometry() %>% 
  filter(flag_peak_time != "Midday")

data_speed_pro_new = data_speed_pro_1 %>%  
  merge(data_speed_pro_stats
        ,by = c("index", "flag_peak_time", "direction_id")) %>% 
  mutate(
    speed_avg = dgt0(speed_avg)
    ,speed_avg_diff = dgt0(speed_avg_diff)
    ,label = str_glue("{direction_id} - {flag_peak_time} - {flag_week_part}\nSeg. Speed (mph): {speed_avg}\nRoute Segment: {index}")
    ,label_map = str_glue("{direction_id} - {flag_peak_time} - {flag_week_part}<br>Seg. Speed (mph): {speed_avg}<br>Route Segment: {index}"))

pal_centroids_od = leaflet::colorNumeric(
      palette = "magma"
      ,data_speed_pro_new$speed_avg
      ,reverse = T)

data_speed_pro_sh = SharedData$new(data_speed_pro_new)

bscols(
  widths = c(2, 10)
  ,list(
    filter_slider("fltr_index", "Route Segment:", data_speed_pro_sh, ~index, step = 5)
    ,filter_slider("fltr_speed_avg", "Point Speed:", data_speed_pro_sh, ~speed_avg, step = 5, round = T)
    ,filter_slider("fltr_speed_avg", "Speed Difference:", data_speed_pro_sh, ~speed_avg_diff, step = 5, round = T)
    ,filter_slider("fltr_speed_avg_mean", "Average Speed:", data_speed_pro_sh, ~speed_avg_mean, step = 5, round = T)
    ,filter_slider("fltr_speed_avg_sd", "Segment SD:", data_speed_pro_sh, ~speed_avg_sd, step = 1, round = T)
    ,filter_slider("fltr_speed_avg_stderr", "Segment SDErr:", data_speed_pro_sh, ~speed_avg_stderr, step = 1, round = T)
    ,filter_slider("fltr_rec_count", "Segment Rec Counts:", data_speed_pro_sh, ~rec_count, step = 1, round = T)
  )
  ,bscols(
    widths = c(3, 3, 3, 7, 5)
    ,filter_select("fltr_direction_id", "Direction:", data_speed_pro_sh, ~direction_id, multiple = T)
    ,filter_select("fltr_flag_peak_time", "Day Peak:", data_speed_pro_sh, ~flag_peak_time, multiple = T)
    ,filter_select("fltr_flag_week_part", "Week Part:", data_speed_pro_sh, ~flag_week_part, multiple = T)
    ,plot_ly(data_speed_pro_sh, x=~index, y = ~speed_avg, alpha = .4
             ,text = ~label, hoverinfo = 'text', height = 600)
    ,leaflet(data_speed_pro_sh, height = 600) %>% 
      leaflet::addTiles(group = "OSM (default)") %>%
      leaflet_default_tiles() %>%
      addCircleMarkers(
        lng = ~lon, lat = ~lat, radius = ~gauntlet::rescale_to(speed_avg, 20)
        ,fillColor = ~pal_centroids_od(data_speed_pro_new$speed_avg), color = "black"
        ,label = data_speed_pro_new$label_map %>% purrr::map(htmltools::HTML)
        ,opacity = .7, fillOpacity  = .6, weight = 1, group = "speeds") %>% 
      leafem::addMouseCoordinates() %>%
      leaflet::addLayersControl(
        baseGroups = gauntlet::leaflet_default_tiles_index()
        # ,overlayGroups = c("speeds")
        ,options = layersControlOptions(collapsed = F, sortLayers = F)) %>% 
      leaflet::addLegend(
        position = "bottomright"
        ,title = "Vehicle Point<br>Speeds (MPH)"
        ,group = "speeds"
        ,pal = pal_centroids_od
        ,opacity = 0.7
        ,values = data_speed_pro_new$speed_avg)
  )
)

```

<style>
.container-fluid.crosstalk-bscols {
margin-left: 30px;
margin-right: 30px;
white-space: normal
}

body>.container-fluid.crosstalk-bscols {
margin-left: auto;
margin-right: auto
}

.crosstalk-input-checkboxgroup .crosstalk-options-group .crosstalk-options-column {
display: inline-block;
padding-right: 12px;
vertical-align: top
}

@media only screen and (max-width: 480px) {
.crosstalk-input-checkboxgroup .crosstalk-options-group .crosstalk-options-column {
display:block;
padding-right: inherit
}
}

.crosstalk-input {
margin-bottom: 15px
}

.crosstalk-input .control-label {
margin-bottom: 0;
vertical-align: middle
}

.crosstalk-input input[type="checkbox"] {
margin: 4px 0 0;
margin-top: 1px;
line-height: normal
}

.crosstalk-input .checkbox {
position: relative;
display: block;
margin-top: 10px;
margin-bottom: 10px
}

.crosstalk-input .checkbox>label {
padding-left: 20px;
margin-bottom: 0;
font-weight: 400;
cursor: pointer
}

.crosstalk-input .checkbox input[type="checkbox"],.crosstalk-input .checkbox-inline input[type="checkbox"] {
position: absolute;
margin-top: 2px;
margin-left: -20px
}

.crosstalk-input .checkbox+.checkbox {
margin-top: -5px
}

.crosstalk-input .checkbox-inline {
position: relative;
display: inline-block;
padding-left: 20px;
margin-bottom: 0;
font-weight: 400;
vertical-align: middle;
cursor: pointer
}

.crosstalk-input .checkbox-inline+.checkbox-inline {
margin-top: 0;
margin-left: 10px
}

</style>





















