---
title: "Daily Reports"

output:
  flexdashboard::flex_dashboard
    # theme: 
    #   version: 4
    #   bootswatch: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, out.width = "100%")
# knitr::opts_chunk$set(
#   cache = FALSE, cache.lazy = FALSE, autodep = TRUE, warning = FALSE, 
#   message = FALSE, echo = TRUE, dpi = 180,
#   fig.width = 5, fig.height = 3, echo = FALSE
#   )
```

<!--#general comments===========================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#
# This is [[insert description here - what it does/solve]]
#
# By: mike gaunt, michael.gaunt@wsp.com
#
# README: [[insert brief readme here]]
#-------- [[insert brief readme here]]
#
# *please use 80 character margins
# *please go to https://pkgs.rstudio.com/flexdashboard/articles/layouts.html
# to explore the different layouts available for the flexdashboard framework
#
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~ -->

<!--#library set-up=============================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev -->
```{r echo=FALSE, message=F}
library(tidyverse)
library(gauntlet)
library(here)
library(magrittr)
library(stringr)
library(readr)
library(purrr)
library(dplyr)
library(jsonlite)
library(rtgtfsr)
library(log4r)
library(sf)
library(leaflet)
library(leafpop)
```

<!--#source helpers/utilities===================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev -->
```{r}
source(here::here("code", "dev_explore_turning_counts.r"))
```

<!--#source data================================================================
#~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~
#content in this section should be removed if in production - ok for dev 
#area to upload data with and to perform initial munging
#please add test data here so that others may use/unit test these scripts -->
```{js}
function filter_default(){
  document.getElementById("id_acct_type").getElementsByClassName("selectized")[0].selectize.setValue("All",false) 
  document.getElementById("id_metric_acct").getElementsByClassName("selectized")[0].selectize.setValue("Acct Count",false) 
  document.getElementById("id_acct_status").getElementsByClassName("selectized")[0].selectize.setValue(["Active", "Pending Close"],false)
  document.getElementById("id_acct_status_wd").getElementsByClassName("selectized")[0].selectize.setValue(["Active", "Pending Close"],false) 
}
    
$(document).ready(filter_default);
```


Accounts Creation 
================================================================================ 

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### By Account Type 
```{r}
int_map
```

### Month Agg.
```{r}

```

Accounts Cycle Day 
================================================================================ 

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### Agg. by Cycle Day {#week-agg}
```{r}

```

### Agg by Account Status {#daily-agg}
```{r}

```

Pass Fulfillment
================================================================================ 

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### By Year/Month
```{r}

```

Daily Posting Summary 
================================================================================ 

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### By Posting Date 
```{r}

```

### By Trip Date 
```{r}

```

CSR Report 
================================================================================ 

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### CSR
```{r}

```

Disposition Summary
================================================================================ 

Row {.tabset .tabset-fade}
--------------------------------------------------------------------------------

### Disposition
```{r}

```

<style>
.container-fluid.crosstalk-bscols {
margin-left: 30px;
margin-right: 30px;
white-space: normal
}

body>.container-fluid.crosstalk-bscols {
margin-left: auto;
margin-right: auto
}

.crosstalk-input-checkboxgroup .crosstalk-options-group .crosstalk-options-column {
display: inline-block;
padding-right: 12px;
vertical-align: top
}

@media only screen and (max-width: 480px) {
.crosstalk-input-checkboxgroup .crosstalk-options-group .crosstalk-options-column {
display:block;
padding-right: inherit
}
}

.crosstalk-input {
margin-bottom: 15px
}

.crosstalk-input .control-label {
margin-bottom: 0;
vertical-align: middle
}

.crosstalk-input input[type="checkbox"] {
margin: 4px 0 0;
margin-top: 1px;
line-height: normal
}

.crosstalk-input .checkbox {
position: relative;
display: block;
margin-top: 10px;
margin-bottom: 10px
}

.crosstalk-input .checkbox>label {
padding-left: 20px;
margin-bottom: 0;
font-weight: 400;
cursor: pointer
}

.crosstalk-input .checkbox input[type="checkbox"],.crosstalk-input .checkbox-inline input[type="checkbox"] {
position: absolute;
margin-top: 2px;
margin-left: -20px
}

.crosstalk-input .checkbox+.checkbox {
margin-top: -5px
}

.crosstalk-input .checkbox-inline {
position: relative;
display: inline-block;
padding-left: 20px;
margin-bottom: 0;
font-weight: 400;
vertical-align: middle;
cursor: pointer
}

.crosstalk-input .checkbox-inline+.checkbox-inline {
margin-top: 0;
margin-left: 10px
}

</style>





















